Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-07 paper.tex
fix typo
write Hamiltonian clock check

We then attempt to construct a 2-local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biomonte_love_2008}.

First, we ensure that the invalid clock states have high eigenvalues. That is, we take $$H_{clock}=\sum_{1\leq i<j\leq T} I\otimes \ket{01}\bra{01}_{ij}$$. We also set $S_{legal}=\ker H_{clock}$.
We note that when stricted to $S_{legal}$, 
\begin{itemize}
	\item $\ket{10}\bra{10}_{t,t+1}
		=\ket{\widehat{t}}\bra{\widehat{t}}$ 
	\item $\ket{1}\bra{0}_{t+1}
		=\ket{\widehat{t+1}}\bra{\widehat{t}}$
	\item $\ket{11}\bra{00}_{t,t+1}
		=\ket{\widehat{t+2}}\bra{\widehat{t}}$
\end{itemize}

>>>>

We then attempt to construct a local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biamonte_love_2008}.

First, we ensure that the invalid clock states have high eigenvalues.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
We also set $S_{legal}=\ker H_{clock}$. Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register. Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates.
$$H_{clock}=\frac{1}{4}((T-1)I + Z_1 - Z_T - \sum_t^{T-1}Z_tZ_{t+1})$$
